---
title: "France Opinion Polls MRP"
author: Gabriel Gilling
---


```{r message=FALSE, warning=FALSE}
options(dplyr.summarise.inform=F) 
library(haven)
library(dplyr)
library(robustHD)
library(ggplot2)
library(forcats)
library(rstanarm)

#v668 IT NUTS 1, v660 FR NUTS 2, v673 NUTS1 UK
#v601 gender v602 age v596 ms

unique(eb75.2$v596)
```

Step 2: Census
```{r}
# census2011_education <- read.csv("https://raw.githubusercontent.com/gabgilling/Thesis/master/Data/census_edu_predictors.csv", header = T)

source("https://raw.githubusercontent.com/gabgilling/Thesis/master/prepare_census.R")
census2011_ms <- read.csv("https://raw.githubusercontent.com/gabgilling/Thesis/master/Data/census_ms_predictors.csv", header = T)

reg_preds <- merge(reg_preds,census2011_ms %>% select(Constituency, Region.Name, country), by = "Region.Name", all.x = TRUE)
# reg_preds$Constituency <-ifelse(is.na(reg_preds$Constituency), reg_preds$Region.Name, reg_preds$Constituency)

reg_preds_constituencies <-  reg_preds %>% group_by(Constituency) %>% 
                                summarise(gdp_cap2 = weighted.mean(gdp_cap, pop),
                                hhd_income2= weighted.mean(hhd_income, pop),
                                unemp_pct2 = weighted.mean(unemp_pct , pop),
                                higher_ed2 = weighted.mean(higher_ed, pop))


census2011_ms[c("gdp_cap2", "hhd_income2", "unemp_pct2", "higher_ed2")] <- NULL

reg_preds_constituencies[c("gdp_cap2", "hhd_income2", "unemp_pct2", "higher_ed2")] <- reg_preds_constituencies[c("gdp_cap2", "hhd_income2", "unemp_pct2", "higher_ed2")] %>% robustHD::standardize()

census2011_ms <-merge(census2011_ms, reg_preds_constituencies, by = "Constituency", all.x = T)


```


Step 3: Get regional and country level predictors

https://ec.europa.eu/eurostat/web/regions/data/database

## add marital status 

https://ec.europa.eu/eurostat/web/rural-development/data

https://www.gesis.org/en/eurobarometer-data-service/search-data-access/topics
https://www.kaggle.com/ruslankl/european-union-lgbt-survey-2012?select=LGBT_Survey_Discrimination.csv

## is having more regional predictors than individual predictors OK?

try to minimize amounts of regional predictors, maybe 2-3

```{r estimate_preferences}

set.seed(1010)



eb75.2 %>% group_by(NUTS_eb) %>% summarise(mean(eu.leg, na.rm = T))



rbind(eb75.2 %>% select(protect.env, age_cat2, gender_male, ms, NUTS_eb), eb81.3 %>% select(protect.env, age_cat2, gender_male, ms, NUTS_eb)) %>% group_by(age_cat2, gender_male, ms, NUTS_eb) %>%
  summarise(pro = sum(get(var_name) == 1), against = n() - pro) %>% na.omit()
```


```{r}
source("/Users/gabgilling/Documents/Documents - Gabriel’s MacBook Pro/GitHub/Thesis/wrange_eb.R")

fit_var_logit <- function(survey_df = c(), var_name, regional_predictors){
  # print(length(survey_df))
  if (length(survey_df) >= 2){
    
    temp <- get(survey_df[1]) %>% select(var_name, age_cat2, gender_male, ms, NUTS_eb)
    for (i in 2:length(survey_df)){
      temp <- rbind(temp, get(survey_df[i]) %>% select(var_name, age_cat2, gender_male, ms, NUTS_eb))
    }
  } else {
    temp = get(survey_df)
  }
  

  temp <- merge(temp, regional_predictors, by = "Constituency", all.x = T)

  temp <- temp %>% group_by(age_cat2, gender_male, ms, Constituency, country, gdp_cap2, 
                            higher_ed2,hhd_income2, unemp_pct2) %>%
                            summarise(pro = sum(get(var_name) == 1), against = n() - pro) %>% 
                            na.omit()
  
  set.seed(1010)

  return(stan_glmer(cbind(pro, against) ~ (1|country) + (1|Constituency) + (1 | age_cat2)  + (1|ms) + gdp_cap2 + gender_male, data = temp, family = binomial(link = "logit"), refresh= 0, 
                    chains = 4, cores=  4, adapt_delta= 0.99))

}



generate_estimates <- function(survey_df){
  excl <- c("gender_male", "age_cat2", "ms" , "year","parliament", "country",
            "Region.Name", "Constituency", "NUTS_eb_old", "NUTS_eb_new")
  
  my_list <- list()
  i <- 1
  for (col in colnames(get(survey_df))[!colnames(get(survey_df)) %in% excl]){
    print(col)
    my_list[[i]] <- fit_var_logit(survey_df = survey_df, var_name = col, 
                                  regional_predictors = reg_preds_constituencies)
    names(my_list)[[1]] <- as.character(col)
    i <- i + 1
  }
  return(my_list)
}

fit.692 <- generate_estimates("eb69.2")
fit.813 <- generate_estimates("eb81.3")
fit.752 <- generate_estimates("eb75.2")
fit.621 <- generate_estimates("eb62.1")
fit.682 <- generate_estimates("eb68.2")
fit.711 <- generate_estimates("eb71.1")
fit.721 <- generate_estimates("eb72.1")
fit.752 <- generate_estimates("eb75.2")

fit.802 <- generate_estimates("eb80.2")
fit.834 <- generate_estimates("eb83.4")

fit.871 <- generate_estimates("eb87.1")

fit.881 <- generate_estimates("eb88.1")
fit.902 <- generate_estimates("eb90.2")


set.seed(1011)
fit.692[[8]] <- fit_var_logit(survey_df = c("eb69.2"), var_name = "ghgtarget")

set.seed(1011)
fit_var_logit(survey_df = c("eb88.1"), var_name = "env.important", reg_preds_constituencies)

print(fit.protect.env, digits = 3)
```

# look into variation of individual questions
# one of the questions that best captures underlying preferences, captures a trade off econ vs. environment 

# take 1 regional level predictor (gdpcap)

```{r poststratify}
census2011_ms$isocntry <- census2011_ms$country

generate_region_estimates <- function(poststrat, fitted_model){
  
  ## generate state_df
  N <- length(unique(poststrat$Constituency))
  
  region_preferences <- data.frame(
                          Constituency = unique(poststrat$Constituency),
                          country = rep("", N),
                          pref = rep(-1, N),
                          se = rep(-1, N)
)

  for (i in unique(poststrat$Constituency)) {
    # print(i)
    poststrat_region <- poststrat[poststrat$Constituency == i, ] %>% na.omit()
    
    posterior_prob_region <- posterior_epred(
      fitted_model,
      # transform = TRUE,
      draws = 1000,
      newdata = as.data.frame(poststrat_region)
    )
    
    poststrat_prob_region <- posterior_prob_region %*% poststrat_region$freq / sum(poststrat_region$freq)

    #This is the estimate for popn in state:
    region_preferences[region_preferences$Constituency == i,]$pref <- round(mean(poststrat_prob_region), 4)
    region_preferences[region_preferences$Constituency == i,]$se <- round(sd(poststrat_prob_region), 4)
    region_preferences[region_preferences$Constituency == i,]$country <- unique(poststrat_region$isocntry)
  }
  
  # return(region_preferences %>% group_by(Constituency, country) %>% summarise(pref = mean(pref), se = mean(se)))
  return(region_preferences)
}

poststrat_survey <- function(model_list){
  survey_prefs <- list()
  agg_results <- generate_region_estimates(poststrat = census2011_ms %>%  na.omit(), model_list[[1]])
  if (length(model_list) == 1){
  return(list(agg_results))
  }
  else {
    survey_prefs[[1]] <- agg_results
    for (i in 2:length(model_list)){
      res <- generate_region_estimates(poststrat = census2011_ms %>%  na.omit(), model_list[[i]])
      survey_prefs[[i]] <- res
      agg_results <- rbind(agg_results, res)
    }
  
    agg_prefs <- as.data.frame(agg_results %>% 
                                 group_by(Constituency, country) %>% 
                                 summarise(mean_pref = mean(pref), mean_se = mean(se)))
  out <- list(agg_prefs, survey_prefs)
  names(out) <- c("agg_prefs", "survey_prefs")
  return(out)
  }
}

prefs.621 <- poststrat_survey(fit.621)
prefs.621[[1]]$year <- 2004
prefs.621[[1]]$parliament <- 6
names(prefs.621) <- c("agg_pref", "question_prefs")
prefs.692 <- poststrat_survey(fit.692)
prefs.692[[1]]$year <- 2008
prefs.692[[1]]$parliament <- 6
names(prefs.692) <- c("agg_pref", "question_prefs")
prefs.813 <- poststrat_survey(fit.813)
prefs.813[[1]]$year <- 2014
prefs.813[[1]]$parliament <- 7
names(prefs.813) <- c("agg_pref", "question_prefs")
prefs.752 <- poststrat_survey(fit.752)
prefs.752[[1]]$parliament <- 7
prefs.752[[1]]$year <- 2011
names(prefs.752) <- c("agg_pref", "question_prefs")
prefs.682 <- poststrat_survey(fit.682)
prefs.682[[1]]$year <- 2007
prefs.682[[1]]$parliament <- 6
names(prefs.682) <- c("agg_pref", "question_prefs")
prefs.711 <- poststrat_survey(fit.711)
prefs.711[[1]]$year <- 2009
prefs.711[[1]]$parliament <- 6
names(prefs.711) <- c("agg_pref", "question_prefs")
prefs.721 <- poststrat_survey(fit.721)
prefs.721[[1]]$year <- 2009
prefs.721[[1]]$parliament <- 7
names(prefs.721) <- c("agg_pref", "question_prefs")
prefs.752 <- poststrat_survey(fit.752)
prefs.752[[1]]$year <- 2011
prefs.752[[1]]$parliament <- 7
names(prefs.752) <- c("agg_pref", "question_prefs")
prefs.802 <- poststrat_survey(fit.802)
prefs.802[[1]]$year <- 2013
prefs.802[[1]]$parliament <- 7
names(prefs.802) <- c("agg_pref", "question_prefs")
prefs.834 <- poststrat_survey(fit.834)
prefs.834[[1]]$year <- 2015
prefs.834[[1]]$parliament <- 8
names(prefs.834) <- c("agg_pref", "question_prefs")
prefs.871 <- poststrat_survey(fit.871)
prefs.871[[1]]$year <- 2017
prefs.871[[1]]$parliament <- 8
names(prefs.871) <- c("agg_pref", "question_prefs")
prefs.881 <- poststrat_survey(fit.881)
prefs.881[[1]]$parliament <- 8
prefs.881[[1]]$year <- 2017
names(prefs.881) <- c("agg_pref", "question_prefs")
prefs.902 <- poststrat_survey(fit.902)
prefs.902[[1]]$year <- 2018
prefs.902[[1]]$parliament <- 8
names(prefs.902) <- c("agg_pref", "question_prefs")



total.prefs <- rbind(prefs.621[[1]],prefs.692[[1]], prefs.813[[1]], prefs.752[[1]], prefs.682[[1]],
                     prefs.711[[1]], prefs.721[[1]],prefs.752[[1]], prefs.802[[1]], prefs.834[[1]],
                     prefs.871[[1]], prefs.902[[1]], prefs.881[[1]]) 

total.prefs$parliament <- ifelse(total.prefs$parliament == 6, "6th Term (2004-2009)", 
                                 ifelse(total.prefs$parliament == 7, "7th Term (2009-2014)", "8th Term (2014-2019)"))

```


```{r}
ggplot(prefs.692[[1]] %>% 
                          group_by(Constituency, country) %>% 
                          summarise(mean_pref = mean(mean_pref), mean_se = mean(mean_se)),
                    aes(x= reorder(Constituency, mean_pref), y = mean_pref, color = country)) + 
                    geom_point() + 
                    geom_errorbar(aes(ymin= mean_pref - mean_se, ymax= mean_pref + mean_se), width=0) +
                    theme_classic() +
                    ggtitle("") +
                    theme(axis.text.x = element_text(angle = 90)) +
                    labs(x = "Constituency", y = "Mean Preference")
```

```{r}
colnames(eb62.1)
excl <- c("gender_male", "age_cat2", "ms" , "year","parliament", "country",
            "Region.Name", "Constituency", "NUTS_eb_old", "NUTS_eb_new", "Constituency")

t <- na.omit(eb62.1) %>% group_by(Constituency, country) %>% 
                summarise_at(colnames(eb62.1[!colnames(eb62.1) %in% excl]), mean)
t <- t[-8]

t

ggplot(cbind(t[c(1:2)], mean_prefs = t[-c(1:2)] %>% rowMeans()), aes( x= Constituency, y = mean_prefs)) + 
  geom_point() +   theme(axis.text.x = element_text(angle = 90)) +
  labs(x = "Constituency", y = "Mean Preference") 

```
```{r}
ggplot(prefs.621[[1]], aes(x = Constituency, y= mean_pref)) + geom_point() +   theme(axis.text.x = element_text(angle = 90)) +
  labs(x = "Constituency", y = "Mean Preference") 

```


I. Get regional level roll call votes. Need to figure out what roll call votes can be correlated to regional level preferences

votewatch.eu/en/term9-european-parliament-latest-votes.html

https://mepsurvey.eu/data-objects/data/

# MEP Survey data

# T4-0084/1995

Final votes tabulated as "Proposition"
Amendments - "Am"

tabulate parliament group activities as additional control

need to adjust for fact that some MEPs were not in parliament at that time

```{r}
# install.packages("rjson")
library(rjson)
MEP.data <- fromJSON(file = "/Users/gabgilling/Dropbox/QMSS/Fall 2020/Thesis/Data/ep_votes.json")

legislation <- read.csv("https://raw.githubusercontent.com/gabgilling/Thesis/master/Data/legislation.csv")
# 
# cond <- sapply(MEP.data, function(x) grepl(legislation$ID[1], x$title))
# 
# cond <- sapply(MEP.data, function(x) grepl("envir", x$title))
# 
# cond.ts <- sapply(MEP.data, function(x) grepl("2018-11", x$ts))

#A8-0354/2018 CO2 emission performance standards for new heavy duty vehicles ***I	
cond1 <- sapply(MEP.data, function(x) grepl("A8-0354/2018", x$title))
dat <- MEP.data[cond1]
cond2 <- sapply(dat, function(x) grepl("Proposition", x$title))
A8.0354 <- dat[cond2][[1]]

#A8-0249/2015 reduction of national emissions of certain atmospheric pollutants
#https://www.europarl.europa.eu/doceo/document/TA-8-2016-0438_EN.html

cond1 <- sapply(MEP.data, function(x) grepl("A8-0249/2015", x$title))
dat <- MEP.data[cond1]
cond2 <- sapply(dat, function(x) grepl("Résolution", x$title))
A8.0249 <- dat[cond2][[1]]

#A8-0317/2018 
#reduction of the impact of certain plastic products on the environment
#https://www.europarl.europa.eu/doceo/document/A-8-2018-0317_EN.html

# A7-0294/2012
# establishment of a Programme for the Environment and Climate Action (LIFE)
# https://www.europarl.europa.eu/doceo/document/A-7-2012-0294_EN.html?redirect

cond3 <- sapply(MEP.data, function(x) grepl(legislation$ID[1], x$title))
dat <- MEP.data[cond3]
cond3 <- sapply(dat, function(x) grepl("roposition|Résolution", x$title))
A7.0294 <- dat[cond3][[1]]
# https://eur-lex.europa.eu/legal-content/en/HIS/?uri=CELEX:32008L0050

legislation_list <- list()

for (i in 1:nrow(legislation)){
  cond <- sapply(MEP.data, function(x) grepl(legislation$ID[i], x$title))
  dat <- MEP.data[cond]
  cond <- sapply(dat, function(x) grepl("roposition|ésolution", x$title))
  try(legislation_list[[i]] <- dat[cond][[1]])
}

cond <- (sapply(MEP.data, function(x) grepl("A7-0191/2012", x$doc)))

for (i in 1:length(MEP.data)){
  try(if (MEP.data[[i]]$votes$`+`$total == 634){
    print(MEP.data[[i]]$title)
  }, silent = T)
}
sapply(MEP.data, function(x) {x == 634}, x$votes$`+`$total)

dat <- MEP.data[[cond]]
```

```{r}
mep.ids <- read.csv("https://raw.githubusercontent.com/gabgilling/Thesis/master/Data/mep_data_with_IDs.csv")


mep.ids$constituency <- ifelse(mep.ids$constituency == "Southern Italy", "South Italy",
                               ifelse(mep.ids$constituency == "Massif-central-Centre", 	    
                                      "Massif-central–Centre", mep.ids$constituency))

mep.ids$Parliament <- as.character(mep.ids$Parliament)
mep.ids$X <- NULL

count_votes <- function(resolution, col_name){
  # initialize 0s for abstained botes
  mep.ids[col_name] <- 0
  
  for (i in resolution$votes$`+`$groups){
    for (id in unname(unlist(i))){
      if (id %in% unique(mep.ids$ID)){
        mep.ids[mep.ids$ID == id,][col_name] <- 1
      }
    }
  }
  
  for (i in resolution$votes$`-`$groups){
    for (id in unname(unlist(i))){
      if (id %in% unique(mep.ids$ID)){
        mep.ids[mep.ids$ID == id,][col_name]- -1
      }
    }
  }
  # set values to NA for MEPs not present during a certain vote
  mep.ids[col_name] <-  with(mep.ids, ifelse(Parliament != substring(col_name, 2,2), NA, get(col_name)))
  return(mep.ids)
}


for (i in 1:length(legislation_list)){
  # some laws were not present in the parltrack database, so ignore them
  if (length(legislation_list[[i]]) != 0){
    # create a column with the law's ID and count votes
    mep.ids <- count_votes(resolution = legislation_list[[i]], legislation_list[[i]]$doc)
  }
}

library(matrixStats)

mep.ids$ID <- as.character(mep.ids$ID)

mep.ids <- mep.ids %>% group_by(constituency, Parliament) %>% 
  ungroup %>% 
  mutate(mean_pref = rowMeans(select(., is.numeric), na.rm = T), 
         mean_sd = apply(select(., is.numeric) ,1, sd, na.rm = TRUE))

#   mutate(newvar = rowSums(select(., starts_with("prefix_"))))

unique(mep.ids$constituency)
```


```{r}
mep_prefs.total <- mep.ids %>% 
         group_by(constituency, country) %>% 
         summarise(mep_pref = mean(mean_pref, na.rm = T))

voter_prefs.total <- total.prefs %>% 
  group_by(Constituency, country) %>% 
  summarise(mean_pref = mean(mean_pref))

reg_df <- merge(mep_prefs.total,voter_prefs.total, by.x = "constituency", by.y = "Constituency", all.y = T)

summary(lm(mep_pref ~ mean_pref + country.x, data = reg_df), digits = 3)

```


```{r}
library(stargazer)
mep_prefs.total.parl <- mep.ids %>% 
         group_by(constituency, country, Parliament) %>% 
         summarise(mep_pref = mean(mean_pref, na.rm = T))

voter_prefs.total.parl <- total.prefs %>% 
  group_by(Constituency, parliament, country) %>% 
  summarise(mean_pref = mean(mean_pref))

reg_df2 <- merge(mep_prefs.total.parl,voter_prefs.total.parl, by.x = c("Parliament", "constituency"), by.y = c("parliament", "Constituency"), all.y = T)

stargazer(lm(mep_pref ~ mean_pref + country.x + as.factor(Parliament), data = reg_df2), title = "Regression Output")
```

```{r warning=FALSE}
library(rgdal)
library(broom)
library(maptools)
library(ggplot2)

# install.packages('rgeos', type='source')
# install.packages('rgdal', type='source')

NUTS_shape = readOGR(dsn = "/Users/gabgilling/Desktop/NUTS_2013_01M_SH/data/")

NUTS_shape2 = readOGR(dsn = "/Users/gabgilling/Desktop/NUTS_2013_01M_SH/data/", layer = "NUTS_RG_01M_2013")

nuts <- readOGR(dsn = "/Users/gabgilling/Desktop/NUTS_2013_01M_SH/data/NUTS_RG_01M_2013.shp")

nuts <- nuts[nuts$STAT_LEVL_ %in% c(1,2),]
nuts <- nuts[grepl("FR|UK|IT",nuts$NUTS_ID),]

# plot(nuts)
shp_df <- fortify(nuts, region = "NUTS_ID")

shp_df <- shp_df %>% filter(id %in% c("FR", "UK", "IT"))

# NUTS_shape2@data$LAT <- NUTS_shape@data$LAT
# NUTS_shape2@data$LON <- NUTS_shape@data$LON
# 
# NUTS_fort <- tidy(NUTS_shape)
ggplot() + geom_polygon(data= shp_df, aes(x = long, y = lat, group = group, color = id))

plot(NUTS_shape)
```

